A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-19 paper/refactor.tex
include new tables in paper structure
delete itemize of similarities and add a paragraph explaining the selection of path

The similarities defined in the nltk-api are the following:

\begin{itemize}
  \item Path Similarity: based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.
  \item Leacock-Chodorow Similarity: based on the shortest path that connects the senses (as above) and the maximum depth of the taxonomy in which the senses occur. The relationship is given as -log(p/2d) where p is the shortest path length and d the taxonomy depth.
  \item Wu-Palmer Similarity: based on the depth of the two senses in the taxonomy and that of their Least Common Subsumer (most specific ancestor node). 
  \item Resnik Similarity: based on the Information Content (IC) of the Least Common Subsumer. Note that for any similarity measure that uses information content, the result is dependent on the corpus used to generate the information content and the specifics of how the information content was created.
  \item Jiang-Conrath Similarity Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets. The relationship is given by the equation 1 / (IC(s1) + IC(s2) - 2 * IC(lcs)).
  \item Lin Similarity: Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets. The relationship is given by the equation 2 * IC(lcs) / (IC(s1) + IC(s2)).
\end{itemize}

@@

\input{handpicked_table}
\section{Results}

% \subsubsection{Top senses for selected works}

\input{results}

>>>>

The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity. \textbf{fill me with shit from the paper}\cite{BUDANITSKY}. In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one). Path similarity was the best in the trade off between the complexity of the measure and the obtained results. This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.

%   \item Leacock-Chodorow Similarity: based on the shortest path that connects the senses (as above) and the maximum depth of the taxonomy in which the senses occur. The relationship is given as -log(p/2d) where p is the shortest path length and d the taxonomy depth.
%   \item Wu-Palmer Similarity: based on the depth of the two senses in the taxonomy and that of their Least Common Subsumer (most specific ancestor node). 
%   \item Resnik Similarity: based on the Information Content (IC) of the Least Common Subsumer. Note that for any similarity measure that uses information content, the result is dependent on the corpus used to generate the information content and the specifics of how the information content was created.
%   \item Jiang-Conrath Similarity Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets. The relationship is given by the equation 1 / (IC(s1) + IC(s2) - 2 * IC(lcs)).
%   \item Lin Similarity: Return a score denoting how similar two word senses are, based on the Information Content (IC) of the Least Common Subsumer and that of the two input Synsets. The relationship is given by the equation 2 * IC(lcs) / (IC(s1) + IC(s2)).
% \end{itemize}

@@

\input{handpicked_table}
\section{Results}
This section is divided in two: first, we present the \textit{top senses} of the documents listed in "Text corpus"; second, we present the similarities between the documents and the word-senses evaluation set.

%\subsubsection{Top senses for selected works}
\input{results}

%\subsubsection{Similarities with chosen concepts}
\input{results_sim_tables}
